experiment 1

### 2021-07-23 experiments/experiment 1/experiment-1.Rmd
Update experiment-1.Rmd

```{r}
num_CB_strains <- 9
num_SB_strains <- 9
num_PB_strains <- 9
CB_gmax_div <- 0.015789474 * 0
CB_h_div <- -0.08 * 0
SB_gmax_div <- 0.015789474 * 5
SB_h_div <- -0.323  * 5
PB_gmax_div <- 0.015789474  * 5
PB_h_div <- -0.323  * 5

@@

```{r}
display_diversity(20)
```

@@

##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)

@@

>>>>

```{r}
num_CB_strains <- 9
num_SB_strains <- 9
num_PB_strains <- 9

## multiplier of SBPB variation
CB_var_multiplier <- 1
SBPB_var_multiplier <- 5

CB_gmax_div <- 0.015789474 * CB_var_multiplier
CB_h_div <- -0.08 * CB_var_multiplier
SB_gmax_div <- 0.015789474 * SBPB_var_multiplier
SB_h_div <- -0.323  * SBPB_var_multiplier
PB_gmax_div <- 0.015789474  * SBPB_var_multiplier
PB_h_div <- -0.323  * SBPB_var_multiplier

@@

```{r}
display_diversity(400)
```

@@

##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
stab_data1 <- readRDS(here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS"))
stab_data_x <- readRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))
stab_data_plus <- bind_rows(stab_data1, stab_data_x)
stab_data_plus %>%
  filter(Species == "O",
         sim_length == 1e6) %>%
  ggplot(aes(x = CB_var_gmax_s, y = SB_var_gmax_s, fill = hyst_range, col = hyst_range)) +
  geom_point(size = 3)

@@

# Understand about relative and absolute variation in traits

```{r echo = FALSE}
num_CB_strains <- 9
num_SB_strains <- 9
num_PB_strains <- 9

## multiplier of SBPB variation
CB_var_multiplier <- 1
SBPB_var_multiplier <- 5

CB_gmax_div <- 0.015789474 * CB_var_multiplier
CB_h_div <- -0.08 * CB_var_multiplier
SB_gmax_div <- 0.015789474 * SBPB_var_multiplier
SB_h_div <- -0.323  * SBPB_var_multiplier
PB_gmax_div <- 0.015789474  * SBPB_var_multiplier
PB_h_div <- -0.323  * SBPB_var_multiplier

num_div_treatment_levels <- 2

var_expt <- create_diversity_factorial()

display_diversity(4)

this_one <- 4
CBtraits <- var_expt$pars[[this_one]]$CB
P <- 1 #10^seq(-5, 5, 0.1)
SR <- 10^seq(0, 3, 0.1)
gr_rateCB1 <- growth1(P, CBtraits$g_max_CB[1], CBtraits$k_CB_P[1]) * inhibition(SR, CBtraits$h_SR_CB[1])
gr_rateCB9 <- growth1(P, CBtraits$g_max_CB[num_CB_strains], CBtraits$k_CB_P[num_CB_strains]) * inhibition(SR, CBtraits$h_SR_CB[num_CB_strains])
CB_gr_rates <- (c(gr_rateCB1, gr_rateCB9))
CB_gr_range <- max(CB_gr_rates) - min(CB_gr_rates)
CB_gr_range

SBtraits <- var_expt$pars[[this_one]]$SB
P <- 1 #10^seq(-5, 5, 0.1)
SO <- 1
O <- 10^seq(-2.5, 2.5, 0.1)
gr_rateSB1 <- growth2(P, SO, SBtraits$g_max_SB[1], SBtraits$k_SB_P[1], SBtraits$k_SB_SO[1]) *
  inhibition(O, SBtraits$h_O_SB[1])
gr_rateSB9 <- growth2(P, SO, SBtraits$g_max_SB[9], SBtraits$k_SB_P[9], SBtraits$k_SB_SO[9]) *
    inhibition(O, SBtraits$h_O_SB[9])
SB_gr_rates <- (c(gr_rateSB1, gr_rateSB9))
SB_gr_range <- max(SB_gr_rates) - min(SB_gr_rates)
SB_gr_range

PBtraits <- var_expt$pars[[this_one]]$PB
P <- 1 #10^seq(-5, 5, 0.1)
SO <- 1
O <- 10^seq(-2.5, 2.5, 0.1)
gr_ratePB1 <- growth2(P, SO, PBtraits$g_max_PB[1], PBtraits$k_PB_P[1], PBtraits$k_PB_SR[1]) *
  inhibition(O, PBtraits$h_O_PB[1])
gr_ratePB9 <- growth2(P, SO, PBtraits$g_max_PB[9], PBtraits$k_PB_P[9], PBtraits$k_PB_SR[9]) *
  inhibition(O, PBtraits$h_O_PB[9])
PB_gr_rates <- (c(gr_ratePB1, gr_ratePB9))
PB_gr_range <- max(PB_gr_rates) - min(PB_gr_rates)
PB_gr_range

With the CB diversity multiplier set at `r CB_var_multiplier` and the SB/PB multiplier set at `r SBPB_var_multiplier` the range of realised growth rates of CB is `r CB_gr_range`, range of SB is `r SB_gr_range`, and range of PB is `r PB_gr_range`.
